An Autonomous and Decentralized Data Marketplace for Trusted Machine Economy $^{\dagger}$

### 2019-12-31 paper.tex
Fix latex compiled error
Remove template comments

%  LaTeX support: latex@mdpi.com 
%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

%=================================================================
\documentclass[journal,article,applsci,submit,moreauthors,pdftex]{Definitions/mdpi} 
\graphicspath{ {./images/} }
% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'. The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, aerospace, agriculture, agriengineering, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, asc, asi, atmosphere, atoms, axioms, batteries, bdcc, behavsci , beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci , buildings, cancers, carbon , catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, children, cleantechnol, climate, clockssleep, cmd, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, dairy, data, dentistry, designs , diagnostics, diseases, diversity, drones, econometrics, economies, education, ejihpe, electrochem, electronics, energies, entropy, environments, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forests, fractalfract, futureinternet, futurephys, galaxies, games, gastrointestdisord, gels, genealogy, genes, geohazards, geosciences, geriatrics, hazardousmatters, healthcare, heritage, highthroughput, horticulturae, humanities, hydrology, ijerph, ijfs, ijgi, ijms, ijns, ijtpp, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmse, jnt, jof, joitmc, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, medicina, medicines, medsci, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, mti, nanomaterials, ncrna, neuroglia, nitrogen, notspecified, nutrients, ohbm, optics, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, physics, plants, plasma, polymers, polysaccharides, preprints , proceedings, processes, proteomes, psych, publications, quantumrep, quaternary, qubs, reactions, recycling, religions, remotesensing, reports, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, smartcities, sna, societies, socsci, soilsystems, sports, standards, stats, surfaces, surgeries, sustainability, symmetry, systems, technologies, test, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wem, wevj

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, conferenceproceedings, correction, conferencereport, expressionofconcern, extendedabstract, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{xx}
\issuenum{1}
\articlenumber{5}
\pubyear{2019}
\copyrightyear{2019}
%\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}
%\updates{yes} % If there is an update available, un-comment this line

%% MDPI internal command: uncomment if new journal that already uses continuous page numbers 
%\continuouspages{yes}

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz
\usepackage{listings}

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{An Autonomous and Decentralized Data Marketplace for Trusted Machine Economy $^{\dagger}$}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

@@

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

@@

% Abstract (Do not insert blank lines, i.e. \\) 
%%%% 200 words
\abstract{Transacting IoT data must be different in many from traditional approaches in order to build much-needed trust in data marketplaces—trust that will be key to their sustainability. Data generated internally to an organization is usually not enough to remain competitive, enhance customer experiences, or improve strategic decision-making. In this paper, we propose a novel approach to construct IoT-enabled data marketplaces via a decentralized and trustless architecture through the posting of trade records while including the transaction process on distributed ledgers. This approach can efficiently enhance the degree of transparency, as all interactions with smart contracts will be written on-chain. Storage via an end-to-end encrypted message channel allows transmitting and accessing trusted data streams over distributed ledgers regardless of the size or cost of the device, while simultaneously making a verifiable Auth-compliant request to the platform. Furthermore, the platform will complete matching, trading and refunding processes without human intervention which also protects the rights of data providers and consumers through a trading policy written on the smart contract, and finally apply evolutionary game theory to the machine economy.}

@@

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%\setcounter{secnumdepth}{4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

@@

% interaction between provider
Data provider is the main role to interact with MAM. With a seed, a provider can start creating a channel or endpoint. As above mentioned, the length of a channel and an endpoint is fixed, thus providers need to decide the selling unit of data products according to its data type or pricing strategy. Also data providers can a make product preview which is public and not encrypted on MAM. In Figure \ref{fig:mam_struct}, a "central endpoint" means its endpoint's ID is the same as channel's ID. By attaching part of the product to central endpoint can give consumers a quick preview with channel's ID only. Then if the trade establishes, providers can then give consumers the encrypted endpoint and session key to consumers. After retrieving the messages on endpoints, users can easily verify the content with digital signatures included in messages.

% why MAM
The decentralized and fault-tolerant charactaristic of distributed ledgers reduce the risks of centralized storage services, and the underlying IOTA network is scalable which withstands real-time data while increasing users all over the world. Moreover, the features of MAM makes it an even better data storage which allows preserving streaming data while ensuring data integrity, proving data ownership to any participants and managing session keys of data. And through the access control and the desing of channel, endpoint of MAM, participants are allowed to subscribe the future data. This ensures that only service requester and selected provider are in possession of a key to decrypt and read the content of the MAM channel and therefore retrieve transaction data for audit.

% efficiency problem of MAM
While the operations of MAM time-consuming, brokers are responsible not only for being the bridge of providers and consumers but for all MAM related operations, such as channel creation and encrypted data publishing in our system. See Figure \ref{fig:launching_product}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Bulleted lists look like this:
%\begin{itemize}[leftmargin=*,labelsep=5.8mm]
%Numbered lists can be added as follows:
%\begin{enumerate}[leftmargin=*,labelsep=4.9mm]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

By combining the established standards and openly-developed specifications, this paper proposed an autonomous data marketplace design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services. It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants and enable secure communication and flexible trading mechanisms.

%Data Auction
The data auction process is a data trading mechanism and an economically-driven scheme that establishes corresponding prices of data products through bidding process between consumers and providers. While there has been many auction models\cite{BigPicDataMarket} in several areas, there has been minimal research on third-party auction platforms. Our proposed decentralized data marketplace protects the privacy of participants which reveals the minimum information for validation and reduces the suspicion of trust to centralized parties or auctioneers. However, the auction process between multiple participants and analysis of potential threats are still critical issues that need to be resolved. For the game theory model presented in this work, we assume each data provider's behavior is independent. However, normally there would be multiple data providers providing similar products (substitutions). Only one provider is taken into considerations at present.

@@

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
\externalbibliography{yes}
\bibliography{references}

%=====================================
% References, variant B: internal bibliography
%=====================================
%\begin{thebibliography}{999}
%\bibliography{references}
% Reference 1
%\bibitem[Author1(year)]{ref-journal}
%Author1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% Reference 2
%\bibitem[Author2(year)]{ref-book}
%Author2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; %Publishing House: City, Country, 2007; pp. 32--58.
%\end{thebibliography}

% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences. For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\sampleavailability{Samples of the compounds ...... are available from the authors.}

%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

>>>>

\documentclass[journal,article,applsci,submit,moreauthors,pdftex]{Definitions/mdpi} 
\graphicspath{ {./images/} }

\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{xx}
\issuenum{1}
\articlenumber{5}
\pubyear{2019}
\copyrightyear{2019}
\history{Received: date; Accepted: date; Published: date}
%\updates{yes} % If there is an update available, un-comment this line

% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz
\usepackage{listings}

\Title{An Autonomous and Decentralized Data Marketplace for Trusted Machine Economy $^{\dagger}$}

@@

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Transacting IoT data must be different in many from traditional approaches in order to build much-needed trust in data marketplaces—trust that will be key to their sustainability. Data generated internally to an organization is usually not enough to remain competitive, enhance customer experiences, or improve strategic decision-making. In this paper, we propose a novel approach to construct IoT-enabled data marketplaces via a decentralized and trustless architecture through the posting of trade records while including the transaction process on distributed ledgers. This approach can efficiently enhance the degree of transparency, as all interactions with smart contracts will be written on-chain. Storage via an end-to-end encrypted message channel allows transmitting and accessing trusted data streams over distributed ledgers regardless of the size or cost of the device, while simultaneously making a verifiable Auth-compliant request to the platform. Furthermore, the platform will complete matching, trading and refunding processes without human intervention which also protects the rights of data providers and consumers through a trading policy written on the smart contract, and finally apply evolutionary game theory to the machine economy.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

Data provider is the main role to interact with MAM. With a seed, a provider can start creating a channel or endpoint. As above mentioned, the length of a channel and an endpoint is fixed, thus providers need to decide the selling unit of data products according to its data type or pricing strategy. Also data providers can a make product preview which is public and not encrypted on MAM. In Figure \ref{fig:mam_struct}, a "central endpoint" means its endpoint's ID is the same as channel's ID. By attaching part of the product to central endpoint can give consumers a quick preview with channel's ID only. Then if the trade establishes, providers can then give consumers the encrypted endpoint and session key to consumers. After retrieving the messages on endpoints, users can easily verify the content with digital signatures included in messages.

The decentralized and fault-tolerant charactaristic of distributed ledgers reduce the risks of centralized storage services, and the underlying IOTA network is scalable which withstands real-time data while increasing users all over the world. Moreover, the features of MAM makes it an even better data storage which allows preserving streaming data while ensuring data integrity, proving data ownership to any participants and managing session keys of data. And through the access control and the desing of channel, endpoint of MAM, participants are allowed to subscribe the future data. This ensures that only service requester and selected provider are in possession of a key to decrypt and read the content of the MAM channel and therefore retrieve transaction data for audit.

While the operations of MAM time-consuming, brokers are responsible not only for being the bridge of providers and consumers but for all MAM related operations, such as channel creation and encrypted data publishing in our system. See Figure \ref{fig:launching_product}.

@@

\section{Conclusions}
By combining the established standards and openly-developed specifications, this paper proposed an autonomous data marketplace design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services. It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants and enable secure communication and flexible trading mechanisms.

The data auction process is a data trading mechanism and an economically-driven scheme that establishes corresponding prices of data products through bidding process between consumers and providers. While there has been many auction models\cite{BigPicDataMarket} in several areas, there has been minimal research on third-party auction platforms. Our proposed decentralized data marketplace protects the privacy of participants which reveals the minimum information for validation and reduces the suspicion of trust to centralized parties or auctioneers. However, the auction process between multiple participants and analysis of potential threats are still critical issues that need to be resolved. For the game theory model presented in this work, we assume each data provider's behavior is independent. However, normally there would be multiple data providers providing similar products (substitutions). Only one provider is taken into considerations at present.

@@

\externalbibliography{yes}
\bibliography{references}

\end{document}
